---
title: "First Package"
author: "Jeff Bone"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Foo Factor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
#Overview
This package is designed to simplify working with factors. It consists of three functions as outlined below. 

#Package Installation
One must first install and load the package. 
```{r}
#install.packages("FirstPackage")
library("FirstPackage")
```

#Data to be Used in Examples
```{r,error=TRUE}
fruit <- c("Apples","Oranges","Bananas")
fruit <- as.factor(fruit)
gourd <- c("Potatoes","Yams","Squash")
gourd <- as.factor(gourd)
veg <- c("Carrots","Bell Peppers","Celery")
veg <- as.factor(veg)
```

#Example of fbind
fbind takes two factors and puts them together into one. The input is two factors and the output is one factor. For example,
```{r,error=TRUE}
#example 1
fbind(fruit,gourd)

#example 2
fbind(veg,fruit)

#example 3
fbind(1,2) #won't run if inputs are not factors
```

#Example of freq_out
freq_out creates a frequency table for a factor. The input must be a factor and the output is a tbl data frame. For example, 
```{r,error=TRUE}
#example 1
fruit_sample <- sample(fruit,20,rep=TRUE)
fruit_sample
freq_out(fruit_sample)

#example 2
veg_sample <- sample(veg,20,rep=TRUE)
combined_fruit_veg <- fbind(fruit_sample,veg_sample)
freq_out(combined_fruit_veg)

#example 3
freq_out(c(1,1,1,1)) #won't run if input is not a factor
```

#Example of reorder_factor
reorder_factor reorders the levels of a factor based on frequency. The input is a factor and the output is the same factor with reordered levels. For example, 
```{r,error=TRUE}
#example 1
veg_sample <- sample(veg,20,rep=TRUE)
veg_sample
reorder_factor(veg_sample)

#example 2
reorder_factor(gourd) #doesn't reorder if all levels have same number

#example 3
reorder_factor(c(1,2,3)) #doesn't run if input is not a factor
```
